\subsection{Dataset}
\label{subsec:dataset}
 An Institutional Review Board (IRB) approved a protocol for retrospective review of MRI exams from patients with biopsy proven prostate cancer. The IRB waived the need for informed consent. A total of 220 consecutive patients, presenting for evaluation for radiation treatment from XXXXX through XXXXXX and scanned on a Discovery MR750 3T MRI (GE, Waukesha, WI, USA) were utilized. In addition, 330 MRI exams, publicly available from the SPIE-AAPM-NCI PROSTATEx Challenge \cite{deukwoo_classification_2018}, acquired on two different types of Siemens 3T MR scanners, the MAGNETOM Trio and Skyra (Siemens, Erlangen, Germany) were considered. All MRI exams included acquisition of T2-w in the axial, coronal and sagittal orientations. Acquisition parameters are given in Supplementary Table 1.
Prostate and PZ were manually contoured on axial T2-w MRI in MIM (MIM Software Inc, Cleveland, OH, USA) by imaging experts (RS, ALB, NG) with more than 30 years combined expertise in prostate cancer. The contours were cross checked by the imaging experts and reviewed by radiation oncologists (MCA, AP) with extensive expertise in genitourinary malignancies.
The imaging data and contours were pre-processed as described below.

% Compared to most publications, this dataset is one of the largest and more heterogeneous ones \cite{anneke,litjens2014evaluation,chowdhury2012concurrent,toth2012multifeature,4_klein2008automatic,5_cheng2014atlas,6_xie2014low,7_tian2015fully,8_korsager2015use,jia20183d}.

